\begin{originality}

Ich erkläre gegenüber der Freien Universität Berlin, dass ich die vorliegende Dissertation selbstständig und ohne Benutzung anderer als der angegebenen Quellen und Hilfsmittel angefertigt habe. Die vorliegende Arbeit ist frei von Plagiaten. Alle Ausführungen, die wörtlich oder inhaltlich aus anderen Schriften entnommen sind, habe ich als solche kenntlich gemacht. Diese Dissertation wurde in gleicher oder ähnlicher Form noch in keinem früheren Promotionsverfahren eingereicht.

\end{originality}

\begin{acknowledgements}

This thesis is written under the supervision of Nicolas Perkowski at Freie Universität Berlin. I would like to thank him for his supervision.\\

I would like to thank Benjamin Gess at TU Berlin for reviewing the thesis. It is a huge honor for me as part of the thesis is written under the influence of his pioneering works with collaborators. I would like to thank the dissertation committee for reviewing the thesis. I would like to thank my collaborators, especially Immanuel Zachhuber, Francesco De Vecchi and Zhengyan Wu, for all the discussions.\\

The motivation of exploring stochastic analysis came from a course by Jean-Dominique Deuschel in TU Berlin, when I was close to finishing a master degree in Econometrics. It was a wonderful and challenging course on large deviation, which changed my interest to probability. \\

I have ever since benefited tremendously from Huanyu Yang, Immanuel Zachhuber and Willem van Zuijlen who were always willing to share their knowledge, as I started to learn singular SPDEs at FU Berlin. I am also grateful to Bernhard Eisvogel, Carlos Villanueva Mariz, Chara Zhu, Da Li, Dave Jacobi, Guilherme de Lima Feltes, Helena Kremp, Huanyu Yang, Henri Elad Altman, Julian Kern, Lucio Galeati, Lukas Gräfner, Ruhong Jin, Shyam Popat, Toyomu Matsuda and Wei Huang for being friendly colleagues in the group. \\

Besides, I am deeply grateful to my stay in the research group Pattern Formation, Energy Landscapes and Scaling Law in the Max-Planck-Institut Leipzig for the profound environment of mathematics and physics created by Felix Otto and other group members. I would like to thank my officemates Anton Ullrich and Xiaopeng Chen for their friendship and Rhys Steele for the fantastic lectures on regularity structures with great passion. It was a great privilege and pleasure to discuss with Björn Bringmann, Lukas Broux, Matteo Palmieri, Max Sauerbrey, Nikolay Barashkov, Thomas Suchanek and Qiang Xu. \\

With Fabian Höfer and Sarah Jean-Meyer, we had the amazing chance to organize a spring school in Münster on singular SPDEs generously supported by the Cluster of Excellence Mathematics Münster, and I am grateful to all lecturers for their wonderful talks. With Fabian Höfer, Ruoyuan Liu, Shao Liu and Xianfeng Ren, we had so many joyful and stimulating talks and discussions on random dispersive equations. I would like to thank Fan Cheng, Yaowei Zhang and Yifan Tang from BMS and FU Berlin for their friendship. I would like to thank all the friends and colleagues that I met in various conferences during my PhD study.\\ 

I am especially indebted to Carlos Villanueva Mariz, Chunqiu Song, Fabian Höfer, Francesco De Vecchi, Henri Elad Altman and Immanuel Zachhuber for all the support they offered when I struggled. \\

Lastly, I would like to thank my family, namely my parents, my grandparents and my wife Fengli. I definitely would not be able to start the doctoral study without the unconditional support from my mom and dad, even though these three years were quite difficult for them; I definitely would not be able to persevere to the end without Fengli being always so supportive, calm and organizing everything in good order. While she has already achieved herself a PhD degree in chemistry with the highest honor from Max–Planck Institute and FU Berlin, her contribution to this one is at least as much as mine. \\ 

I grew up in a graceful suburban town Jiading\footnote{The figure following is an AI-modified woodcut print of the Huilongtan, Jiading in 1890s from OpenAI’s DALL·E (2025).} in Northwest Shanghai as the only child and spent most of my childhood in the company of my grandparents carefreely, owing to their tranquil nature and almost spoiling love. My grandmothers passed away during my doctoral study. The thesis is therefore dedicated to them for having alway been there for me. 

\end{acknowledgements}

\makepicturepage